\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Broderick Westrope} \\ \vspace{3pt}
    \small
    \href{mailto:broderickwestrope@gmail.com}{\faEnvelope \hspace{.5pt} \underline{broderickwestrope@gmail.com}}
    $|$
    \href{https://linkedin.com/in/broderick-westrope}{\faLinkedinSquare \hspace{.5pt} \underline{LinkedIn}}
    $|$
    \href{https://github.com/broderick-westrope}{\faGithub \hspace{.5pt} \underline{GitHub}}
    $|$
    \href{https://www.westrope.dev/}{\faGlobe \hspace{.5pt} \underline{Website}}
    $|$
    \faMapMarker \hspace{.5pt} Sydney, NSW
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{Nov. 2024 - Present}
      {DroneShield}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Lead the design, implementation, and testing of the company's SAPIENT protocol implementation, reducing the average integration time for SAPIENT-compliant sensors by 97\%.}
        \resumeItem{Used my understanding of Go concurrency to remove 100\% of the panics from the codebase within 12 weeks of starting, resulting in the system having 100\% less crashes per day.}
        \resumeItem{Assisted the delivery lead by translating customer and QA feedback into tickets with acceptance criteria.}
        \resumeItem{Shared my knowledge of developer best practices with the team lead and implemented these changes, reducing the average time for ticket closure by 1 hour per story point.}
      \resumeItemListEnd
      \vspace{5pt}

    \resumeSubheading
      {Software Engineer \& Consultant}{Dec. 2022 - Nov. 2024}
      {Mantel Group}{Sydney, NSW}
      \resumeItemListStart
        \resumeItem{Spearheaded projects with ASP.NET (C\#) to architect, uplift, and migrate REST APIs.}
        \resumeItem{Created long-lived API workflows using Go, Temporal, gRPC, and Connect RPC.}
        \resumeItem{Actively contributing to the Go community through presenting at meetups and conferences, engaging in internal knowledge-sharing, and leading personal training sessions.}
        \resumeItem{Contributed to CI/CD pipeline development, authoring of technical documentation, and motivating TDD.}
        \resumeItem{Key driver of an internal project leveraging Azure DevBox, Azure Bicep \& ARM templates, GitHub Actions, and Terraform for a cutting-edge Azure technology offering.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Engineer}{Jul. 2022 - Dec. 2022}
      {MARCS Institute For Brain Behaviour \& Development}{Westmead, NSW}
      \resumeItemListStart
            \resumeItem{Spearheaded the development of a Unity and C\# cross-platform application for Macular Degeneration treatment, driving the project to success amidst a team with limited technological proficiency.}
            \resumeItem{Implemented innovative features, including authentication, eye-tracking technology, and activity-based assessments, significantly enhancing patient diagnosis and treatment monitoring.}
            \resumeItem{Enabled data-driven therapy decisions by securely collecting and analysing user performance data, directly contributing to the application's adoption by health professionals for improved patient care.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------OTHER PROJECTS-----------
\section{Other Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Soothe}}{Mar. 2025 - Present}
        \resumeItemListStart
          \resumeItem{A full-stack AI service being designed, built, and deployed by me for \href{https://harmonyhealthcare.com.au/}{\underline{Harmony Healthcare}}.}
          \resumeItem{Leverages \href{https://ai.azure.com/}{\underline{Azure AI Foundry}} to equip users with the tools to live a fuller life amidst their chonic pain.}
          \resumeItem{Partnered with Microsoft through their Founders Program, providing me with resources, support, and professional development.}
        \resumeItemListEnd
    % \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Tetrigo}}{Nov. 2023 - Present}
        \resumeItemListStart
          \resumeItem{An interactive TUI (Terminal User Interface) for playing Tetris in your terminal. Built using \href{https://github.com/charmbracelet/bubbletea}{\underline{Bubble Tea}}.}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Open Source}}{Long Term; Ongoing}
        \resumeItemListStart
          \resumeItem{I enjoy contributing to a range of open-source projects owned by others; see \href{https://github.com/broderick-westrope}{\underline{here}} for a list of projects.}
          % \resumeItem{My GitHub profile is up to date and provides insight into projects I'm currently interacting with.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western Sydney University}{Parramatta, NSW}
      {Bachelor of Science in Computer Science}{Dec. 2022}
      \resumeItemListStart
        \resumeItem{On the Dean's Merit List every year.}
        \resumeItem{GPA: 6.23/7}
      \resumeItemListEnd
      
    \resumeSubheading
      {TAFE}{St Leonards, NSW}
      {Diploma in Programming Digital And Interactive Games}{Dec. 2020}

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Go, Dart, C\#, TypeScript, HTML/CSS} \\
     \textbf{Frameworks \& Libraries}{: Temporal, Connect RPC, Vue 3, Flutter, ASP.NET Core, Blazor} \\
     \textbf{Cloud \& DevOps}{: Azure, AWS, Docker, GitHub Actions, Azure DevOps, Buildkite, GitLab} \\
     \textbf{AI Development \& Tooling}{: Azure AI Foundry, Azure Prompt Flows, OpenRouter, Claude} \\
     \textbf{Software Development Methodologies}{: Test-Driven, Cloud-Native, and On-Premises} \\
     \textbf{Database Technologies}{: PostgreSQL, MySQL, Microsoft SQL Server} \\
    }}
 \end{itemize}

\end{document}

